%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Phi}{Nguyen}
{ \urlstyle{same}\href{https://phinguyen.dev}{phinguyen.dev }| \href{https://github.com/pnguy55}{ My GitHub}\\
\href{mailto:phi@phinguyen.dev}{phi@phinguyen.dev} | 225-205-6210
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IBM}
\descript{Apprenticeship - \\}
\location{Application Development\\}
\location{Feb 2020 | Baton Rouge, LA}
\sectionsep

\subsection{Louisiana State University}
\descript{90 Credits towards CS}
\location{May 2013 | Baton Rouge, LA}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Portfolio:// \href{https://phinguyen.dev}{\bf Phi Nguyen} \\
Facebook:// \href{https://facebook/dd}{\bf Phi} \\
GitHub:// \href{https://github.com/pnguy55}{\bf pnguy55}\\
LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\bf phihongnguyen} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Course Work}

\subsection{Apprenticeship}
Agile Software Development  \\
Software Engineering \\
Full Stack JavaScript \\
Relational Database Management \\
API Development \\
React & Redux Development \\
CS50 Harvard Course \\
Cloud Computing \\
SAP Data Migration \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\subsection{Undergraduate}
Data Structures and Algorithms \\
Object Oriented Programming  \\
Video Game Design \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 10000 lines:}
JavaScript \textbullet{}   Java \textbullet{} SQL\\
\location{Over 5000 lines:}
C \textbullet{} C\# \textbullet{} CSS \textbullet{} Dart \textbullet{} Python \\
\location{Frameworks/Tools:}
React \textbullet{} UI5 \textbullet{} HanaXS \textbullet{} Android \textbullet{} Flutter \textbullet{} Postman \textbullet{} MySQL \textbullet{} SAP Hana \textbullet{} GraphQL \textbullet{} GIT
\sectionsep

\subsection{Other Skills}
\textbullet{} Premiere Pro (Video Editing) \\
\textbullet{} Photoshop \\
\textbullet{} Social Media & Email Marketing \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{IBM}
\descript{| Full Stack Software Development Consultant }
\location{June 2019 - Present | Baton Rouge, LA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed solutions written with JavaScript(UI5)/HanaXS/SQL for businesses to handle data migration needs.
\item Meshed with many development teams in an agile environment.
\end{tightemize}
\sectionsep

\runsubsection{Murphy Law Firm}
\descript{| Full Stack JavaScript Developer }
\location{Aug 2018 – Jul 2019 | Baton Rouge, LA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led a small team, 1 developer intern and 2 graphic designers to deliver multiple web projects.
\item Wrote and reviewed code for JS - jQuery, Front-End and PHP backend .
\end{tightemize}
\sectionsep

\runsubsection{Stacks Marketing}
\descript{| Web Developer }
\location{April 2018 – July 2019 | Baton Rouge, LA}
\begin{tightemize}
\item Developed web solutions for small businesses, including groups a website for LSU.
\item \href{https://msg.lsu.edu}{\bf msg.lsu.edu}
\item Fostered client relations to win more business.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\bf Developer Community Experience}
\runsubsection{\href{https://youtube.com/codephony}{Codephony} -}
\descript{Youtube Channel}
I am passionate about helping green developers create a new life for themselves through the self learning process.  \\
My channel statistics: \\
\textbullet{} \href{https://youtube.com/codephony}{\bf youtube.com/codephony}\\
\textbullet{} 500+ Subscribers\\
\textbullet{} Views > 41,000 \\
\textbullet{} Watch Time > 2,300 hours \\

\section{Projects and Accomplishments}
\runsubsection{Deluxe Corp. -}
\descript{IBM Client}
\location{Feb 2020 – May 2020 | Minneapolis, MN}
Developed a JavaScript/SQL solution with \textbf{Desmond Herpin} to help \textbf{Deluxe} keep their revenue records up to date as their data migration was performed over the course of the next year.
\sectionsep

\runsubsection{Norfolk Southern -}
\descript{IBM Client}
\location{May 2020 – June 2020 | Atlanta, GA}
Led the development of a passive data governance tool with JavaScript and SQL.  They were be able to check the tool and run a series of business rules to determine if their data was clean.
\sectionsep

\runsubsection{MyVideoTagger.com -}
\descript{Personal Project}
\location{May 2020 – June 2020 | Atlanta, GA}
Personal project that allows content creators to pull tags from similiar youtube videos to add to their own.  Users can log in with  oAuth and save their taglists to their personal account. \\
\href{https://myvideotagger.com}{\bf MyVideoTagger.com}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
